%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}

\begin{document}
\header{jennifer}{page}{software architect}

% In the aside, each new line forces a line break
\begin{aside} % In the aside, each new line forces a line break
  \section{contact}
    119 Peterborough St.
    Apartment \#25
    Boston, MA 02215
    ~
    (978) 290-0361
    ~
    \hspace{-2ex}\href{mailto:jenipage1989@gmail.com}{jenipage1989@gmail.com}
    \hspace{-5ex}\href{https://github.com/jmpage}{https://github.com/jmpage}
  \section{programming languages}
    Scala, Elixir, Ruby, Java, JavaScript, C, \& C++
  \section{frameworks}
    Scalaz, Cats, Shapeless, Ruby on Rails, \& Opscode Chef
  \section{interests}
    Data Processing,
    Distributed Systems,
    Functional Reactive Programming, \& Type Level Programming
\end{aside}

\section{experience}

\begin{entrylist}
  \entryalt
  {Mar 2017--Present}
  {Lola}
  {Boston, Massachusetts}
  {Software Architect}
  {Developed best practices, engineering processes, team lead for many
    projects \\
    Accomplishments:
    \begin{itemize}
    \item Gathered requirements for and led design and implementation
      of trips product
    \item Gathered requirements for and led design and implementation
      of back office processing system
    \item Led two engineers to improve the quality and accuracy of our
      booking data (as reflected in airline PNRs) as well as reduce
      the burden on our custom support team. We finished our project
      on time, delivering several features ahead of schedule. These
      included the ability to completly import an airline PNR into our
      system and the ability to reflect changes on any part of a
      booking
    \item Closely mentored two junior engineers and provided suport to
      many others, across teams
    \item Standardized and socialized best practices for GraphQL API
      design and implementation, including the usage of delayed
      execution to improve performance
    \item Centralized and automated deployment for most backend
      services and coordinated with devops as their team grew to hand
      over responsibility
    \item Wrote a tool which performed black box performance testing
      on a third party API. Analyzed the resulting data and made
      recommendations which were used to improve our strategy for
      maximizing flight search performance.
    \item Centralized and automated deployment for most backend
      services and coordinated with devops as their team grew to hand
      over responsibility.
    \item Centralized and automated database migrations across all
      databases, eliminating problems previously caused by human error
      and minimizing knowledge required to perform migrations
      correctly.
    \item Consulted with product on and advocated for future
      performance and design improvements.
    \item Quickly investigated and fixed backend bugs encountered by
      the support team, eventually becoming the de facto "goto" person
      for bugs and receiving recognition.
    \item Advocated for, scheduled and coordinated team building
      lunches to improve cohesion
    \end{itemize}
  }
  \entryalt
  {Mar 2015--Mar 2017}
  {Localytics}
  {Boston, Massachusetts}
  {Senior Software Engineer}
  {Full stack engineer focusing primarily on backend to develop and
    maintain a realtime data ingestion system. \\
    Accomplishments:
    \begin{itemize}
      \item Designed new datapoint validation and enrichment pipeline
        with the goal of reducing faults and increasing
        maintainability.
      \item Led architectural design and implementation of improvements
        to profiles product.
      \item Automated post-fault recovery of several services,
        significantly reducing late-night pages and engineering
        burden.
      \item Engaged in architectural discussions for other systems.
      \item Led and helped teach guild for Functional Reactive
        Programming and Type Level Programming.
      \item As crew lead, led two other engineers in shipping
        Re-marketing v1.
      \item Mentored other developers in Scala and Ruby on Rails.
      \item Collaborated with and assisted devops team with design and
        architecture of permissions escalation/approval system which
        helped reduce workload on devops and empowered engineers to take
        devops work into their own hands.
    \end{itemize}
  }
  \entryalt
    {June 2013--Mar 2015}
    {PayPal}
    {Boston, Massachusetts}
    {Software Engineer II}
    {Full stack engineer on a team which provides a Ruby on Rails based UI and API for managing offers and campaigns for PayPal Media Network, Bill Me Later and the PayPal Deals website. \\
    Accomplishments:
    \begin{itemize}
      \item Rewrote part of our application to increase reliability of synchronization with external services.
      \item Addressed security issues within our application and introduced the use of brakeman, a static code analysis tool, to our team's definition of done to help find potential issues before code review.
      \item Mentored new team members and coops using TDD and pair programming.
      \item Collaborated with stakeholders to ensure that our team took on features with the highest business value.
      \item Took ownership of a project to move our team's application to an OpsCode Chef based infrastructure pipeline. Organized milestones and a timeline which broke down the project into small pieces to allow the team to work concurrently. Aided our sister team in moving their application to the same pipeline through training and helping plan the move.
      \item Maintained a >99\% uptime for our application and increased test coverage to >95\% along with my team.
      \item Set up and configured a Jenkins server for continuous integration, security audits, deployments and creating releases.
      \item Presented a tech talk about Rabbit MQ and topic exchanges to help other teams understand how to bind their queues to our exchange to receive messages.
      \item Served as the Vice Chair of the Boston chapter of eBay Women in Technology (eWIT)
    \end{itemize}}
  \entryalt
    {2012}
    {PayPal}
    {Boston, Massachusetts}
    {Summer Intern}
    {Accomplishments:
    \begin{itemize}
      \item Wrote a Sinatra based Ruby application for visualizing ops data for the systems team.
      \item Automated a report generation process that previously required a day to do manually.
    \end{itemize}}
\end{entrylist}

\section{open source contributions}

{\href{https://github.com/gilt/jerkson}{\textbf{jerkson}}} \hfill
{\footnotesize\addfontfeature{Color=lightgray} Scala} \\
Rewrote and re-added test suite to fork of Codahale's jerkson library,
bumped version of jackson dependency, incorporated various bug fixes
from disparate forks.

{\href{https://github.com/seratch/AWScala}{\textbf{AWScala}}} \hfill
{\footnotesize\addfontfeature{Color=lightgray} Scala} \\
Added support for specifying credentials via \verb|ClientConfiguration|.

{\href{https://github.com/ensime/ensime-emacs}{\textbf{ensime-emacs}}}
\hfill{\footnotesize \addfontfeature{Color=lightgray} Lisp} \\
Various contributions to improve the ENSIME (Enhanced Scala and java
Interaction Mode for text Editors) integration for Emacs.

{\href{https://github.com/jmpage/capistrano_scm_nexus}{\textbf{capistrano\_scm\_nexus}}} \hfill {\footnotesize\addfontfeature{Color=lightgray} Ruby Gem} \\
Published a gem which allows Capistrano to deploy a release by downloading an artifact from Sonatype Nexus instead of using SCM.

{\href{https://github.com/newrelic/rpm}{\textbf{newrelic\_rpm}}} \hfill {\footnotesize\addfontfeature{Color=lightgray} Ruby Gem} \\
Added Capistrano 3 support for deployment notification.

{\href{https://github.com/thoughtbot/shoulda-matchers}{\textbf{shoulda-matchers}}} \hfill {\footnotesize\addfontfeature{Color=lightgray} Ruby Gem} \\
Fixed a bug in the \verb|validates_numericality_of| matcher and added a \verb|validates_absence_of| matcher.

\section{education}

\begin{entrylist}
  \entryoneline
    {May 2013}
    {Bachelor {\normalfont of Computer Science}}
    {Worcester Polytechnic Institute}
\end{entrylist}

\end{document}
